No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete

### 2014-01-17 main/LICS.tex
minor edits

\section{Encoding constraint graphs}

\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Hearn-Demaine-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \textsc{PSPACE}-hardness reductions.
%
A rewriting step is the reversal of a single edge in a \emph{constraint graph}, a graph with weighted, directed edges and an \emph{inflow constraint} on each vertex, preserving the condition that the total weight of the incoming edges of each vertex is at least its inflow constraint.
%
The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.

We will introduce minor adaptations to this formalism to suit our reduction to MLL proof equivalence.
%
Mainly, a constraint graph here will have \emph{undirected} edges, and a separate notion of \emph{configuration} imposes a direction on edges.
%
A constraint graph will then be encoded as a sequent, while a configuration corresponds to a linking.
%
In addition, a configuration will be allowed to be \emph{partial}, leaving some edges undirected, as long as the directed edges suffice to satisfy the inflow constraints.

\begin{definition} 
A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,v,w)$ consists of a set $V$ of vertices with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$, and a set $E$ of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.

A (partial) \emph{configuration} of an \textsc{ncg} is a (partial) function $\gamma\colon E\to V$ such that
\begin{itemize}
	\item
for every edge $e$, $\gamma(e)\in v(e)$ or (in the partial case) $\gamma(e)$ is undefined, and
	\item
for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
\end{itemize}

A \emph{reconfiguration step} $\gamma\sim\delta$ connects two (partial) configurations for an \textsc{ncg} $G$ that differ in the assignment of exactly one edge.

The \emph{(partial) \textsc{ncg}-reconfiguration problem} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.

@@

\begin{IEEEproof}
There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
%
Firstly, if $\gamma\sim\delta$ are partial configurations, they may be completed to total configurations $\gamma'\sim\delta'$ or $\gamma'=\delta'$.
%
Secondly, if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by re-assigning the values where they disagree.
%
\end{IEEEproof}

For a graph $G=(V,E,c,v,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
\[
	|c| = \sum_{v\in V}c(v) \qquad |w| = \sum_{e\in E}w(e)~.
\]

>>>>

\section{Encoding constraint logic}

\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \textsc{PSPACE}-hardness reductions.
%
A rewrite step consists of the reversal of a single edge in a \emph{constraint graph}, a graph with weighted, directed edges and an \emph{inflow constraint} on each vertex.
%
Rewrite steps must preserve the condition that the total weight of the incoming edges of each vertex is at least its inflow constraint.
%
The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.

We will introduce minor adaptations to this formalism to suit our reduction to MLL proof equivalence.
%
Mainly, a constraint graph here will have \emph{undirected} edges, and a separate notion of \emph{configuration} imposes a direction on edges.
%
A constraint graph will then be encoded as a sequent, while a configuration corresponds to a linking.
%
In addition, we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.

\begin{definition} 
A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges, between vertices $v(e)=\{v_1,v_2\}\subseteq V$ and with \emph{weight} $w\colon E\to\mathbb N$.
%of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.

\smallskip

A \emph{(partial) configuration} for an \textsc{ncg} is a (partial) function $\gamma\colon E\to V$ such that
\begin{itemize}
	\item
for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$,
	\item
for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
\end{itemize}

\smallskip
A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for an \textsc{ncg} $G$ that differ in value (or definedness) on exactly one edge.
%
\end{definition}

\emph{(Partial) \textsc{ncg}-reconfiguration} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.

@@

\begin{IEEEproof}
Partial \textsc{ncg}-reconfiguration simulates \textsc{ncg}-reconfiguration:
%
%There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
%
firstly, if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\sim\delta'$ or $\gamma'=\delta'$; secondly,
%
if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by reversing the edges on which they disagree.
%
\end{IEEEproof}

\subsection*{Encoding constraint graphs}

For a constraint graph $G=(V,E,c,v,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
\[
	|c| = \sum_{v\in V}c(v) \qquad |w| = \sum_{e\in E}w(e)~.
\]
